|

### 2024-10-24 output/seminar-slideshow.qmd
Create complex items data frame

# Generate data for simple and complex factorial structures
simple_item_loadings <- tribble(
  ~item, ~factor, ~loading,
  'I1',  'F1',    ITEM_BASE_LOADING,
  'I2',  'F1',    ITEM_BASE_LOADING + ITEM_DIST,
  'I3',  'F1',    ITEM_BASE_LOADING + 2 * ITEM_DIST,
  'I4',  'F2',    ITEM_BASE_LOADING,
  'I5',  'F2',    ITEM_BASE_LOADING + ITEM_DIST,
  'I6',  'F2',    ITEM_BASE_LOADING + 2 * ITEM_DIST
)
complex_item_loadings <- simple_item_loadings                                |>
  bind_rows(tibble(item = 'I3', factor = 'F2', loading = ITEM_BASE_LOADING)) |>
  complete(item, factor, fill = list(loading = 0))

@@

```

>>>>

# Generate data for simple and complex factorial structures
simple_item_loadings <- tribble(
  ~item, ~factor, ~loading,
  'I1',  'F1',    ITEM_BASE_LOADING,
  'I2',  'F1',    ITEM_BASE_LOADING + ITEM_DIST,
  'I3',  'F1',    ITEM_BASE_LOADING + 2 * ITEM_DIST,
  'I4',  'F2',    ITEM_BASE_LOADING,
  'I5',  'F2',    ITEM_BASE_LOADING + ITEM_DIST,
  'I6',  'F2',    ITEM_BASE_LOADING + 2 * ITEM_DIST
)
complex_item_loadings <- simple_item_loadings |> bind_rows(
  tibble(
    item    = 'I3',
    factor  = 'F2',
    loading = ITEM_BASE_LOADING - 2 * ITEM_DIST # Secondary loading smaller
  )
)

@@

complex_item_loadings <- complex_item_loadings |>
  complete(item, factor, fill = list(loading = 0))
```
